True Lies

### 2019-08-26 GSV-comment-brief.Rmd
Mention truelies package when bayesian-heads-cts.R is sourced
Add DESCRIPTION, remove checkpoint
add binder comment to Rmd file

# set to TRUE to (re)create the simulations CSV file, then stop:
rerun_java <- FALSE

@@

library(checkpoint)
checkpoint("2018-11-03", scanForPackages = cache_results)

@@

source("bayesian-heads-cts.R")
source("GSV-heads.R")

>>>>

# set to TRUE to (re)create the simulations CSV file, then stop:
# NB: you can't do this within binder AFAIK
rerun_java <- FALSE

@@

@@

suppressMessages(source("bayesian-heads-cts.R"))
source("GSV-heads.R")
